### 2016-05-27 papers/thesis-vischer/Thesis.tex
cleanup all around, fixes, slight content expansion for results and TI Tests skipped!

\subsection{Hard Sphere}
The hard sphere model approximates monoatomic fluids as having no interactions other than collisions. These spheres exhibit no attraction, and consequently each carries kinetic energy $K = 3/2 k_b T$. Further, with no attraction, there is excess internal energy, implying the excess free energy is purely entropic. The system is defined to have zero total linear momentum, and any collision between two or more spheres is perfectly elastic.

\subsubsection{Carnahan-Starling Equation of State}
In order to determine the filling fraction step size during thermodynamic integration we must find changes in filling fraction that yield a suitably-sized change in the system's absolute free energy. To do this we use the Carnahan-Starling equation of state, shown in Eq.~\ref{C-S-eq}.
\begin{align}
    F_{exc}(\eta) &= \frac{4\eta - 3\eta^2}{(1-\eta)^2} N k_b T  
    \label{C-S-eq}  
\end{align} 
where $\eta$ is the filling fraction, $N/V$. The Carnahan-Starling equation of state was developed to model hard spheres at low densities in the thermodynamic limit. We are very much concerned with cells significantly far from the thermodynamic limit. Thankfully, the Carnahan-Starling equation of state is still an excellent approximation at low to moderate filling fractions.\\

@@

The potential energy of the fluid is then always an integer multiple of the well depth $\epsilon$. This leads us to choose $\epsilon$ and $\sigma$ as natural scales for the quantities of our simulation. We then define dimensionless temperatures $T/\epsilon$, energies $E/\epsilon$, and distances $r/\sigma$. Moreover, we make the decision to work in geometric units for coding simplicity, setting the Boltzmann constant $k_B$ to one. This then allows us to reasonably compare energies and temperatures since they have the same units.

@@

We begin by imagining a cell of length $L$ and volume $L^3$ in which lives a particle. Then, we quantize the allowed wavelengths of the particle within the cell by defining the wavevector $\mathbf{k}$ as
\begin{align}
    \mathbf{k} &= \frac{2\pi}{L}(n_x\mathbf{\hat{x}} + n_y\mathbf{\hat{y}} + n_z\mathbf{\hat{z}})
\end{align}
Remembering that kinetic energy can be expressed as $K = \frac{\hbar^2 k^2}{2m}$, and using our definition of $\mathbf{k}$:
\begin{align}
    Z_{id} &= \frac{1}{N!}\left[\int_s V\, \diff\mathbf{p} ~e^{-\beta \frac{\hbar^2 k^2}{2m}}\right]^{N}
    \label{Zt_def}
\end{align}
This unfortunately introduces a mass quantity into the partition function which adds an additional parameter that needs to be determined to properly account for quantum mechanical effects. If we then allow the cell to become very large, then the we can easily see in Eq. \ref{Zt_def} that the spacing between occupants in phase space becomes small, so we can integrate instead $\diff ^3 n$ over all possible values of $n$:
\begin{align}
    Z_{id} &= \frac{1}{N!}\left[\int_0^\infty \diff^3 n ~e^{-\frac{\beta \hbar^2}{2m} \left(\frac{2\pi}{L}(n_x\mathbf{\hat{x}} + n_y\mathbf{\hat{y}} + n_z\mathbf{\hat{z}}\right)^2}\right]^{N} \\
    &= \frac{1}{N!}\left[\int_0^\infty \diff^3 n ~e^{ \frac{-2\beta \hbar^2\pi^2}{mL^2}(n_x^2 + n_y^2 + n_z^2)}\right]^{N}
\end{align}
where extra factors of $\hbar $and$ \pi$ were gained from the change of variables. Evaluating this integral yields
\begin{align}
    Z_{id} &= \left(\frac{V^N}{N!\Lambda^{3N}}\right) \,, \\
    \Lambda &= \frac{\hbar\sqrt{2\pi}}{\sqrt{mT}}
\end{align}
where we have introduced the thermal deBroglie wavelength $\Lambda$ which defines the de Broglie wavelength of an ideal gas at a temperature $T$. The full partition function for any monoatomic system is then
\begin{align}
    Z &= Z_{exc} \left(\frac{V}{N!\Lambda^{3}}\right)^{N} \,.
\end{align}
For liquids, the $Z_{exc}$ factor is difficult to evaluate; the hard sphere liquid, the simplest model for a dense fluid, does not have an analytic representation for the excess free energy. It follows that a considerable amount of work is required to determine the excess free energy for a given system. The absolute free energy, by way of Eq. \ref{FdefSM}, now has the form
\begin{align}
    F_{abs} &= -T\,\ln\left(Z_{exc} \frac{V^N}{N!\Lambda^{3N}}\right)\\
    &= -T\ln\left(Z_{exc}\right)\, -T\left(\frac{V}{(N!)^{1/N}\Lambda^3} \right)^N\\
    &= -T\ln\left(Z_{exc}\right) - NT\ln\left(\frac{V}{\Lambda^3}\right) + NT\ln\left(N!^{1/N}\right)\\ 
\end{align}
Redefining the first factor including $Z_{exc}$ to be $F_{exc}$, and then using Sterling's approximation ($\ln(N!) = N\ln N$ for large N), we arrive at
\begin{align}
    F_{abs} &= F_{exc} - NT\left(\ln\left(\frac{V}{\Lambda^3}\right) - \ln\left(N\right)\right)
\end{align}
At a specified volume and number of particles, the ideal gas contribution is only a function of temperature. Consequently, for a given temperature we only need to compute the excess free energy.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                            METHODS                                  %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Statistical mechanics, however, does not exhibit this independence. Each time the drunken man makes a move there is an equal probability that he will move in any particular direction. Rather than all movements having equal probability, statistical mechanics stipulates that the probability of a particular move occurring depends explicitly upon the energy difference of the current and resulting configurations. Instead of true random Monte Carlo methods, we clearly need some way to control the probability of transitions from a given state. In pursuit of this control, we employ the method of Markov chains, specifically Broad histogram transition matrix Monte Carlo.
\subsubsection{Metropolis-Hastings}
Metropolis-Hastings Monte Carlo methods eschew the true randomness of unbiased Monte Carlo by taking the current configuration into account before moving. If we define the ensemble of states of the system in equilibrium by a vector column $\mathbf{q}$, and the resulting state $\mathbf{p}$ after a single time step, the relationship
\begin{align*}
    \mathbf{p} &= \mathcal{P}\, \mathbf{q}\\
\end{align*}
defines a ``transition'' of the system. $\mathcal{P}$ is a necessarily square matrix that contains information about these transitions. We call this construction $\mathcal{P}$ the {\it transition matrix}. This matrix is $L\times L$, where $L$ is the number of energy levels in system. If all rows of the transition matrix are , we can see that any state of the system is reachable after a finite number of transitions from any given initial state. A physically correct simulation will generate a transition matrix that satisfies the thermodynamic steady state condition; given the ensemble of equilibrium states $\mathbf{q}_{eq}$, we enforce that
\begin{align}
    \mathcal{P}\,\mathbf{q}_{eq} &= \mathbf{q}_{eq}
    \label{thermo-steady-state}
\end{align}
The transition matrix thus embodies the physics of the simulation.

@@

\subsection{Thermodynamic Integration}
\subsubsection{General Process}
Thermodynamic integration is a unique way to determine the ``excess'' free energy of the system. Using hard sphere Monte Carlo, we transition from a filling fraction of zero to a dense system with filling fraction $\eta_{max}$, calculating the change in free energy at each step. When we have reached the desired final filling fraction we have found the free energy that was necessary to create that configuration of particles - this is exactly the absolute free energy of the system.\\
\subsubsection{Algorithm}
The hard sphere fluid is simple to work with since its partition function simply counts the number of microstates in the system\cite{valeskethesis}. Since we are calculating the change in free energy as we transition to higher and higher filling fractions, we need only be concerned with finding the ratio of partition functions between each step. Since the hard sphere partition function is a ``counting'' mechanism, we can determine this ratio quite easily using Monte Carlo simulations. Given a starting state (defined by the arrangement of particles and filling fraction) we shrink the volume and intermolecular distances by a somewhat arbitrary scaling factor and then see if the resulting configuration of particles is valid. If the configuration is valid, we accept this is a working move and then return to the original configuration and test another scaling factor. If the resulting configuration is invalid, we count the move as failed and then repeat. The ``golden'' acceptance ratio is fifty percent - when we have found a scaling factor that yields a ratio near the desired value\dots\\

As with the Monte Carlo these simulations are written in $C++$ for efficiency.

\begin{algorithm}[!b]
\caption{Thermodynamic integration.}
\label{alg:ti}
\begin{alg}
\item Construct cell with desired number of spheres with filling fraction of zero.
\item Move spheres random fractions of a predefined translation distance. \label{alg-ti-move}
\item Repeat step \ref{alg-ti-move} for [desired number of iterations before small cell check].
\item After [desired number of iterations], check the ``small cell'' by shrinking the volume and checking whether or not the configuration is still valid.
\item If configuration is still valid, valid checks ++.
\item If configuration is invalid, failed checks ++. \label{alg-ti-move-end}
\item Repeat steps \ref{alg-ti-move} - \ref{alg-ti-move-end} until desired iterations reached.

@@

\ignore{Should I detail the algorithm itself and string simulations together or consider the entire process $\eta=0\rightarrow\eta_max$ to be the algorithm?}

\ignore{is the distinction between infinite case and regular necessary? we always use infinite...}

\begin{figure} \centering
    \resizebox{.75\textwidth}{!}{
    \begin{tikzpicture}[scale=.8,  auto]
    \draw[blue, ultra thick] (10,3) rectangle (14,7);
    \draw[blue, ultra thick, dashed] (0,1) rectangle (8,9);
    \draw[blue, ultra thick] (16,4.375) rectangle (17.25,5.625);
    \draw[->] (4,8) to (4, 8.85);
    \draw[->] (7,5) to (7.85, 5);
    \draw[->] (1,5) to (.15, 5);
    \draw[->] (4,2) to (4, 1.15);
    \draw[ultra thick, ->] (8.5,5) to (9.5,5);  
    \node [above] at (9,5.25) {\small $k$ steps};
    \draw[ultra thick, ->] (14.5,5) to (15.5,5);
    \node[align=center] [above] at (15, 5.25) {\small $n-k$ \\[-1em] steps};
    \draw[ultra thick, fill=red] (3.5,4.25) circle [radius=.25];
    \draw[ultra thick, fill=red] (6,3.75) circle [radius=.25];
    \draw[ultra thick, fill=red] (5.5,6) circle [radius=.25];
    \draw[ultra thick, fill=red] (10.5,4.5) circle [radius=.25];
    \draw[ultra thick, fill=red] (13,3.5) circle [radius=.25];
    \draw[ultra thick, fill=red] (11,6) circle [radius=.25];
    \draw[ultra thick, fill=red] (16.3,5.3) circle [radius=.25];
    \draw[ultra thick, fill=red] (17,4.75) circle [radius=.25];
    \draw[ultra thick, fill=red] (16.25,4.65) circle [radius=.25];
    \node [above] at
     (4,9) {$\eta_0 \approx 0$};
    \node [above] at (12,7) {$\eta_k$};
    \node [above] at (16.675,5.625) {$\eta_f$}; 
\end{tikzpicture}}
\caption{Demonstration of filling fraction increase during thermodynamic integration from $\eta=0$ to $\eta=\eta_f=\eta_{max}$.}
\end{figure}

@@

Figures ~\ref{F-T} through ~\ref{F-eta} show several computed thermodynamic quantities for the scrunched system. Each plot contains calculations from the first doubling regime ($L=2\lambda_0$) represented by solid lines and second doubling regime ($L = 4\lambda_0$) in dashes. It is worth noting that the succeeding plots with respect to density have been interpolated; with a fixed cell size, it is only possible to simulate discrete filling fractions. The intervening points have been filled in using the Carnahan-Starling equation of state.\\  
\begin{figure}  
\centering
    \includegraphics[width=.75\textwidth]{../renormalization/figs/Fexc-vs-T.pdf}
    \caption{Excess specific free energy as a function of temperature with each quantity scaled by well depth $\epsilon$. }
    \label{F-T}
\end{figure}

@@

Finding coexistence requires use of the grand free energy $\Phi$. Liquid and vapor are simultaneously present in the fluid at densities that cause local minima in the grand free energy. We know that the grand free energy has a guaranteed minimum at the origin because [things]; we then only need to identify the other minima.  \\

Referring back to Eq.~\ref{Phidef}, we can compute an absolute grand free energy given the absolute free energy and number of spheres. The chemical potential $\mu$ is a somewhat unintuitive quantity that, for our purposes, we will treat as a free parameter. Tweaking the value of the chemical potential will allow us to easily identify second minima in the density curve. 
\begin{figure}
\centering
    \includegraphics[width=.75\textwidth]{../renormalization/figs/Phiabs-vs-eta.pdf}
    \caption{Absolute specific free energy as a function of density.}
    \label{Phi-eta}
\end{figure}

Figure \ref{Phi-eta}, \dots.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                             CONCLUSION                         %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\subsection{Hard Sphere}
The hard sphere model approximates fluids as having no interactions other than collisions. These spheres exhibit no attraction, and consequently each carries kinetic energy $K = 3/2 k_b T$. Further, with no attraction, there is no excess internal energy, implying the excess free energy is purely entropic. The system is defined to have zero total linear momentum, and any collision between two or more spheres is perfectly elastic.

\subsubsection{Carnahan-Starling Equation of State}
In order to determine the filling fraction step size during thermodynamic integration we must find changes in filling fraction that yield a suitably-sized change in the system's absolute free energy. To do this we use the Carnahan-Starling equation of state, shown in Eq.~\ref{C-S-eq}.
\begin{align}
    F_{exc}(\eta) &= N k_B T\,\frac{4\eta - 3\eta^2}{(1-\eta)^2}   
    \label{C-S-eq}  
\end{align} 
where $\eta$ is the filling fraction, $N/V$. The Carnahan-Starling equation of state was developed to model hard spheres at low densities in the thermodynamic limit. We are very much concerned with cells significantly far from the thermodynamic limit. Thankfully, the Carnahan-Starling equation of state is still an excellent approximation at low to moderate filling fractions.\\

@@

This leads us to choose $\epsilon$ and $\sigma$ as natural scales for the quantities of our simulation. We then define dimensionless temperatures $T/\epsilon$, energies $E/\epsilon$, and distances $r/\sigma$. Moreover, we make the decision to work in geometric units for coding simplicity, setting the Boltzmann constant $k_B$ to one. This then allows us to reasonably compare energies and temperatures since they have the same units.

@@

We begin by imagining a cell of length $L$ and volume $L^3$ in which lives a particle. Then, we quantize the allowed wavelengths of the particle within the cell by defining the wavevector $\mathbf{k}$ as
\begin{align}
    \mathbf{k} &= \frac{2\pi}{L}(n_x\mathbf{\hat{x}} + n_y\mathbf{\hat{y}} + n_z\mathbf{\hat{z}})
\end{align}
Remembering that kinetic energy can be expressed as $K = \frac{\hbar^2 k^2}{2m}$, and using our definition of $\mathbf{k}$:
\begin{align}
    Z_{id} &= \frac{1}{N!}\left[\int_s V\, \diff\mathbf{p} ~e^{-\beta \frac{\hbar^2 k^2}{2m}}\right]^{N}
    \label{Zt_def}
\end{align}
This unfortunately introduces a mass quantity into the partition function which adds an additional parameter that needs to be determined to properly account for quantum mechanical effects. If we then allow the cell to become very large, then the we can easily see in Eq. \ref{Zt_def} that the spacing between occupants in phase space becomes small, so we can integrate instead $\diff ^3 n$ over all possible values of $n$:
\begin{align}
    Z_{id} &= \frac{1}{N!}\left[\int_0^\infty \diff^3 n ~e^{-\frac{\beta \hbar^2}{2m} \left(\frac{2\pi}{L}(n_x\mathbf{\hat{x}} + n_y\mathbf{\hat{y}} + n_z\mathbf{\hat{z}}\right)^2}\right]^{N} \\
    &= \frac{1}{N!}\left[\int_0^\infty \diff^3 n ~e^{ \frac{-2\beta \hbar^2\pi^2}{mL^2}(n_x^2 + n_y^2 + n_z^2)}\right]^{N}
\end{align}
where extra factors of $\hbar $and$ \pi$ were gained from the change of variables. Evaluating this integral yields
\begin{align}
    Z_{id} &= \left(\frac{V^N}{N!\Lambda^{3N}}\right) \,, \\
    \Lambda &= \frac{\hbar\sqrt{2\pi}}{\sqrt{mT}}
\end{align}
where we have introduced the thermal deBroglie wavelength $\Lambda$ which defines the de Broglie wavelength of an ideal gas at a temperature $T$. The full partition function for any monoatomic system is then
\begin{align}
    Z &= Z_{exc} \left(\frac{V}{N!\Lambda^{3}}\right)^{N} \,.
\end{align}
For liquids, the $Z_{exc}$ factor is difficult to evaluate; the hard sphere liquid, the simplest model for a dense fluid, does not have an analytic representation for the excess free energy. It follows that a considerable amount of work is required to determine the excess free energy for a given system. The absolute free energy, by way of Eq. \ref{FdefSM}, now has the form
\begin{align}
    F_{abs} &= -T\,\ln\left(Z_{exc} \frac{V^N}{N!\Lambda^{3N}}\right)\\
    &= -T\ln\left(Z_{exc}\right)\, -T\ln\left(\frac{V}{(N!)^{1/N}\Lambda^3} \right)^N\\
    &= -T\ln\left(Z_{exc}\right) - NT\ln\left(\frac{V}{\Lambda^3}\right) + NT\ln\left(N!^{1/N}\right)\\ 
\end{align}
Redefining the first factor including $Z_{exc}$ to be $F_{exc}$, and then using Sterling's approximation ($\ln(N!) = N\ln N - N$ for large N), we arrive at \textcolor{red}{BRENDEN FIX: $N\ln N - N$, plus I think we may want to add to the excess free energy (probably to the excess HS entropy?) the difference?}
\begin{align}
    F_{abs} &= F_{exc} - NT\left(\ln\left(\frac{V}{\Lambda^3}\right) - \ln\left(N\right) + 1\right)
\end{align}
At a specified volume and number of particles, the ideal gas contribution is only a function of temperature. Consequently, for a given temperature we only need to compute the excess free energy.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                            METHODS                                  %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Statistical mechanics, however, does not exhibit this independence. Each time the drunken man makes a move there is an equal probability that he will move in any particular direction. Rather than all movements having equal probability, statistical mechanics stipulates that the probability of a particular move occurring depends explicitly upon the energy difference of the current and resulting configurations. Instead of true random Monte Carlo methods, we clearly need some way to control the probability of transitions from a given state. In pursuit of this control, we employ the method of Markov chains, specifically broad histogram transition matrix Monte Carlo.
\subsubsection{Metropolis-Hastings}
Metropolis-Hastings Monte Carlo methods eschew the true randomness of unbiased Monte Carlo by taking the current configuration into account before moving. If we define the ensemble of states of the system in equilibrium by a vector column $\mathbf{q}$, and the resulting state $\mathbf{p}$ after a single time step, the relationship
\begin{align*}
    \mathbf{p} &= \mathcal{P}\, \mathbf{q}\\
\end{align*}
defines a ``transition'' of the system. $\mathcal{P}$ is a necessarily square matrix that contains information about these transitions. We call this construction $\mathcal{P}$ the {\it transition matrix}. This matrix is $L\times L$, where $L$ is the number of energy levels in system. If all rows of the transition matrix are , we can see that any state of the system is reachable after a finite number of transitions from any given initial state. A physically correct simulation will generate a transition matrix that satisfies the thermodynamic steady state condition; given the ensemble of equilibrium states $\mathbf{q}_{eq}$, we enforce that
\begin{align}
    \mathcal{P}\,\mathbf{q}_{eq} &= \mathbf{q}_{eq}
    \label{thermo-steady-state}
\end{align}
The transition matrix thus embodies the physics of the simulation.

@@

\subsection{Thermodynamic Integration}
\subsubsection{General Process}
Thermodynamic integration is a unique way to determine the ``excess'' free energy of the system. Using hard sphere Monte Carlo, we transition from a filling fraction of zero to a dense system with filling fraction $\eta_{max}$, calculating the change in free energy at each step. When we have reached the desired final filling fraction we have found the free energy that was necessary to create that configuration of particles - this is exactly the absolute free energy of the system.\\
\subsubsection{Algorithm}
The hard sphere fluid is simple to work with since its partition function simply counts the number of microstates in the system\cite{valeskethesis}. Since we are calculating the change in free energy as we transition to higher and higher filling fractions, we need only be concerned with finding the ratio of partition functions between each step. Since the hard sphere partition function is a ``counting'' mechanism, we can determine this ratio using Monte Carlo simulations. Given a starting state (defined by the arrangement of particles and filling fraction) we shrink the volume and intermolecular distances by a scaling factor and then see if the resulting configuration of particles is valid. If the configuration is valid, we accept it as also valid in the small cell and then return to the original configuration. If the resulting configuration is invalid, we count the move as failed. This process continues until a predefined number of iterations are completed.\\

Once a count of valid and failed moves for a given filling fraction step has been established, the entropy of the system can be determined. Give $N_i$ total checks of the small cell during the $i^{\text{th}}$ step, $M_i$ of which were valid, the entropy calculated integrating from a filling fraction of $\eta=0$ to some $\eta_f$ in $K$ steps is
\begin{align}
    S_{HS,~exc} &= \sum_i^K \ln\left(\frac{M_i}{N_i-M_i}\right)
\end{align}

\begin{algorithm}[!b]
\caption{Thermodynamic integration.}
\label{alg:ti}
\begin{alg}
\item Construct cell with desired number of spheres with filling fraction of zero.
\item Move spheres random fractions of a predefined translation distance. \label{alg-ti-move}
\item Repeat step \ref{alg-ti-move} for desired number of iterations before checking the small cell.
\item Check the ``small cell'' by shrinking the volume and determine whether or not the configuration is still valid.
\item If configuration is still valid, increment the count of valid checks.
\item If configuration is invalid, increment the count of failed checks. \label{alg-ti-move-end}
\item Repeat steps \ref{alg-ti-move} - \ref{alg-ti-move-end} until desired iterations reached.

@@

%TIKZ
\begin{figure} \centering
    \resizebox{.75\textwidth}{!}{
    \begin{tikzpicture}[scale=.8,  auto]
    \draw[blue, ultra thick] (10,3) rectangle (14,7);
    \draw[blue, ultra thick, dashed] (0,1) rectangle (8,9);
    \draw[blue, ultra thick] (16,4.375) rectangle (17.25,5.625);
    \draw[->] (4,8) to (4, 8.85);
    \draw[->] (7,5) to (7.85, 5);
    \draw[->] (1,5) to (.15, 5);
    \draw[->] (4,2) to (4, 1.15);
    \draw[ultra thick, ->] (8.5,5) to (9.5,5);  
    \node [above] at (9,5.25) {\small $k$ steps};
    \draw[ultra thick, ->] (14.5,5) to (15.5,5);
    \node[align=center] [above] at (15, 5.25) {\small $n-k$ \\[-1em] steps};
    \draw[ultra thick, fill=red] (3.5,4.25) circle [radius=.25];
    \draw[ultra thick, fill=red] (6,3.75) circle [radius=.25];
    \draw[ultra thick, fill=red] (5.5,6) circle [radius=.25];
    \draw[ultra thick, fill=red] (10.5,4.5) circle [radius=.25];
    \draw[ultra thick, fill=red] (13,3.5) circle [radius=.25];
    \draw[ultra thick, fill=red] (11,6) circle [radius=.25];
    \draw[ultra thick, fill=red] (16.3,5.3) circle [radius=.25];
    \draw[ultra thick, fill=red] (17,4.75) circle [radius=.25];
    \draw[ultra thick, fill=red] (16.25,4.65) circle [radius=.25];
    \node [above] at
     (4,9) {$\eta_0 \approx 0$};
    \node [above] at (12,7) {$\eta_k$};
    \node [above] at (16.675,5.625) {$\eta_f$}; 
    \end{tikzpicture}}
    \caption{Demonstration of filling fraction increase during thermodynamic integration from $\eta=0$ to $\eta=\eta_f=\eta_{max}$.}
    \label{TI-demo}
\end{figure}

@@

Figures ~\ref{F-T} through ~\ref{F-eta} show several computed thermodynamic quantities for the scrunched system. Each plot contains calculated quantities for either the first two doubling regimes or the first three. Calculations from the first doubling regime ($L=\lambda_0$) are solid lines, with the second doubling regime ($L = 2\lambda_0$) in dashes and the third ($L = 4\lambda_0$), when present, in circles . It is worth noting that the succeeding plots with respect to density have been interpolated; with a fixed cell size, it is only possible to simulate discrete filling fractions. The intervening points have been filled in using the Carnahan-Starling equation of state.\\  
\begin{figure}  
\centering
    \includegraphics[width=.75\textwidth]{../renormalization/figs/Fexc-vs-T.pdf}
    \caption{Excess specific free energy as a function of temperature.}
    \label{F-T}
\end{figure}

@@

Finding coexistence requires use of the grand free energy $\Phi$. Liquid and vapor are simultaneously present in the fluid at densities that cause local minima in the grand free energy. We know that the grand free energy has a guaranteed minimum at the origin because [things]; we then only need to identify the other minimum.  \\

Referring back to Eq.~\ref{Phidef}, we can compute an absolute grand free energy given the absolute free energy and number of spheres. The chemical potential $\mu$ is a somewhat unintuitive quantity that, for our purposes, we will treat as a free parameter. Tweaking the value of the chemical potential will allow us to easily identify second minima in the grand free energy, and thereby the densities of the liquid and vapor present in the system.
\begin{figure}
\centering
    \includegraphics[width=.75\textwidth]{../renormalization/figs/Phiabs-vs-eta.pdf}
    \caption{Absolute grand free energy as a function of density.}
    \label{Phi-eta}
\end{figure}
Figure \ref{Phi-eta} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                             CONCLUSION                         %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-05-27 papers/thesis-vischer/abstract.tex
cleanup all around, fixes, slight content expansion for results and TI Tests skipped!

\thispagestyle{plain}
\begin{center}
    \Large
    \textbf{Application of Generalized Renormalization Group Methods to the Square-Well Liquid Near Criticality}

@@

You take a box, stuff it with spheres, move them around, make it bigger, do it again. Win grant.
\clearpage

>>>>

\thispagestyle{plain}
\begin{center}
    \Large
    \textbf{Free Energy Decomposition of the Critical Square-Well Liquid Using a Renormalization Group Method}

@@

Analytic models using renormalization methods to approximate the free energy of fluids have been developed, but there is currently no way to investigate the intermediate steps of the approximation. We present a computational method to determine the free energy contributions of each length scale by exploiting both the behavior of the critical fluid and the periodicity of Metropolis-Hastings Monte-Carlo simulations. We further detail a method by which to compute the ``absolute'' free energy, including both the ideal gas free energy and the excess free energy. We further present an application of this method to the well-research square-well liquid near the critical region. We find that the square-well liquid is well-characterized by a base cell length of $\sqrt2\sigma$, the side length of an FCC lattice, by establishing liquid-vapor coexistence between scaled temperatures $0.5 \leq T < .75$.   
\clearpage
